2023 \hspace{58pt} Recipient, Distinguished Researcher Award from the UTSW President’s Research Council
2022 \hspace{58pt} Inductee, Weed High School Hall of Fame. \\
2018 \hspace{58pt} Dean's Discretionary Award, UT Southwestern Medical Center.  \\
2018 \hspace{58pt} Runner-Up, UTSW Brown-Goldstein Excellence in Postdoctoral Research. \\
2016 \hspace{58pt} Nominee, AAAS/Science Program for Excellence in Science.  \\
2015 \hspace{58pt} Finalist, 2015 Educational Award, Edmund Optics. \\
2011 \hspace{58pt} Certificate of Achievement, Colorado Photonics Industry Association (CPIA). \\
2007 \hspace{58pt} Excellence in Graduate Teaching. \\
2007 \hspace{58pt} ESPN \& CoSIDA District 8 Academic All-American. \\
2007 \hspace{58pt} Inducted into National Football Foundation Hampshire Honor Society.  \\
2007 \hspace{58pt} Co-Recipient, Henry Booth Outstanding Senior Male Athlete Award. \\
2006 \hspace{58pt} Willamette University Bill Trenbeath Award. \\
2006 \hspace{58pt} ESPN \& CoSIDA District 8 Academic All-American. \\
2006 \hspace{58pt} Sigma Alpha Epsilon National Scholar. \\
2006 \hspace{58pt} Willamette University Athlete of The Month.\\
2006 \hspace{58pt} Northwest Conference Athlete of the Week. \\
2006 \hspace{58pt} Willamette University Football Team Captain. \\
2005 \hspace{58pt} Invited to Speak at the Murdock's NW Undergraduate Research Meeting. \\
2005 \hspace{58pt} Willamette University Football Team Captain. \\
2005 \hspace{58pt} Peterson Family Scholarship for Chemistry. \\
2005 \hspace{58pt} Inducted into the Mortar Board National Honor Society.  \\
2004 \hspace{58pt} Sigma Alpha Epsilon National Scholar.  \\
2004 \hspace{58pt} Inducted into the National Society of Collegiate Scholars (NSCS).  \\
2004 \hspace{58pt} Selected for Science Collaborative Research Program. \\
2002 \hspace{58pt} Haynes McHale Award.  \\
2002 \hspace{58pt} Neal Wade Award - Weed High School Outstanding Male Athlete of the Year. \\
2002 \hspace{58pt} Inducted into California Scholarship Federation.