\begin{enumerate}
[leftmargin=!,
labelindent=0pt,
itemindent=-66pt,
label=\textbullet]


\item 2024 -- 2025 
\hspace{8pt}
Mechanisms Underlying Lobular Breast Cancer Metastasis to Bone. \\
Charles Pak Family Cancer \& Bone Initiative Research Grant. \\
{\it Co-PI}
%$100,000 = $0.1M

\item 2024 -- 2025 
\hspace{8pt}
Advanced 3D Microscopy for Early Cancer Detection and Tissue-Based Diagnosis. \\
Lyda Hill Philanthropies. \\
Co-PI \\ 
%$100,000 = $0.1M

\item 2024 -- 2025 
\hspace{8pt}
Novel Pharmacologic Strategies to Mitigate Post-Traumatic Extremity Complications \\
Trauma Research and Combat Casualty Care Collaborative \\
Co-I \\ 
%$100,000 = $0.1M

\item 2023 -- 2024 
\hspace{8pt}
Illuminating the Molecular and Cellular Origins of Tissue Function in Health \& Disease.\\
President’s Research Council, UTSW.\\
{\it PI}
%$100,000

\item 2023 -- 2024 
\hspace{8pt}
Next-Generation Histopathology Using Rapid Ultraviolet Photoacoustical Microscopy. \\
Harold C. Simmons Comprehensive Cancer Center, UTSW. \\
{\it MPI}
%$100,000

\item 2022 -- 2023 
\hspace{8pt}
Mechanisms of Cell Rearrangements During Germband Extension in D. Melanogaster.\\
National Institute of Child Health and Human Development, NIH. \\
R21HD105189 \\
{\it Collaborator}
%$457,000

\item 2022 -- 2023 
\hspace{8pt}
Linking Function, Structure, and Molecular Identity of Lateral Habenula Neurons. \\
National Institute of Mental Health, NIH. \\
R34NS121873 \\
{\it Collaborator}
%$737,531

\item 2021 -- 2026 
\hspace{8pt}
UTSW Cancer Center Support Grant \\
National Cancer Institute, NIH. \\
P30CA142543 \\ 
{\it Key Personnel}
%$40,423,323

\item 2020 -- 2025 
\hspace{8pt} 
Prune Belly Syndrome: Mechanisms of Filamin A Mutations. \\
National Institute of Diabetes and Digestive and Kidney Diseases, NIH. \\
R01DK127589 \\
{\it Co-Investigator} 
% $2,519,857

\item 2020 -- 2024
\hspace{8pt} 
Neuronal Signaling Mechanisms of Stress-Induced Anhedonia in the Lateral Habenula. \\
National Institute of Mental Health, NIH. \\
R01MH120131 \\ 
{\it Collaborator}
%$2,413,356

\item 2019 -- 2020 
\hspace{8pt} 
Laser for Ultra-Deep Intravital Imaging.\\
National Institute of General Medical Sciences, NIH. \\
S10OD026722 \\
{\it Key Personnel}
%$250,000

\item 2016 -- 2018 
\hspace{8pt} 
Symmetry breaking and polarization of cells in 3D environments.\\
National Institute of General Medical Sciences, NIH.\\
F32GM117793 \\
{\it Principal Investigator} 
%$120,000

\item 2011 -- 2013 
\hspace{8pt}
Integrative Graduate Education and Research Trainee (IGERT)\\
Computational, Optical, Sensing and Imaging.\\
Division Of Graduate Education, NSF \\
0801680\\
{\it Trainee}

\item 2009 -- 2011
\hspace{8pt}
Interdisciplinary Predoctoral Training in Molecular Biophysics. \\
National Institute of General Medical Sciences, NIH. \\
T32GM065103 \\
{\it Trainee}

\item 2006 -- 2007 
\hspace{8pt} 
Sigma Xi Undergraduate Research Fellowship. \\
{\it Trainee}

\end{enumerate}
