\begin{enumerate}
\item Kevin M. Dean.  EPFL Latsis Symposium 2024. Lausanne, Switzerland. 2024.
\item Kevin M. Dean.  American Society for Cell Biology (ASCB). Virtual. 2021.
\item Kevin M. Dean.  Society for Neuroscience (SfN). Virtual. 2021.
\item Kevin M. Dean.  EMBO \& EMBL Symposium: Seeing is Believing - Imaging the Processes of Life.  Virtual.  2021.
\item Doug P. Shepherd, Alfred Millett-Sikking, Andrew G. York, Reto P. Fiolka, Kevin M. Dean.  Focus On Microscopy. Virtual. 2021.
\item Kevin M. Dean, Denise Ramirez, Reto Fiolka, Hu Zhao, and Kate Luby-Phelps. Arizona Imaging and Microanalysis Conference. Virtual. 2021.
\item Tonmoy Chakraborty, Reto Fiolka, and Kevin M. Dean.  The Network of European Bioimage Analysts (NEUBIAS).  Bordeaux, France. 2020.
\item Kevin M. Dean.  Imaging Mouse Development.  Janelia Farm, Howard Hughes Medical Institute.  Ashburn, VA, USA. 2020.
\item Alfred Millett-Sikking, Andrew G. York, Reto Fiolka, Kevin M. Dean.  Focus On Microscopy.  Osaka, Japan. {\it Cancelled}. 2020.
\item Kevin M. Dean.  The Academy of Medicine, Engineering \& Science of Texas (TAMEST).  Dallas, TX, USA. 2020.
\item Tonmoy Chakraborty, Reto Fiolka, and Kevin M. Dean.  EMBL Seeing is Believing. Heidelberg, Germany. 2019.
\item Kevin M. Dean. Frontiers and Challenges in Laser-Based Biological Microscopy. Telluride, CO, USA. 2019.
\item Tonmoy Chakraborty, Bo-Jui Chang, Kevin M. Dean, and Reto Fiolka.  Focus On Microscopy.  London, U.K.  2018.
\item Kevin M. Dean, Tadamoto Isogai, Philippe Roudot, Erik S. Welf, Meghan K. Driscoll, Reto Fiolka, and Gaudenz Danuser.  Focus On Microscopy.  Singapore, Republic of Singapore. 2018.
\item Kevin M. Dean, Erik S. Welf, Philippe Roudot, Meghan K. Driscoll, Reto Fiolka, and Gaudenz Danuser.  Frontiers in Imaging Science.  Janelia Farm, Howard Hughes Medical Institute.  Ashburn, VA, USA.  2017.
\item Kevin M. Dean, Erik S. Welf, Philippe Roudot, Meghan K. Driscoll, Reto Fiolka, and Gaudenz Danuser.  Biophysical Society.  New Orleans, LA, USA. 2017.
\item Kevin M. Dean, Erik S. Welf, Philippe Roudot, Meghan K. Driscoll, Reto Fiolka, and Gaudenz Danuser.  Quantitative BioImaging 2017.  College Station, TX, USA. 2017.
\item Kevin M. Dean et al,  Microscope Technologies for Quantitative Imaging in 3D Microenvironments.  {\it SPIE, Biomedical Optics and Medical Imaging}.  2016.
\item Kevin M. Dean and Reto Fiolka. Isotropic 3D Imaging over Large Volumes with Axially Swept Light-Sheet Microscopy.  {\it inFocus Magazine, Royal Microscopical Society}.  2016.
\item Kevin M. Dean, Erik S. Welf, Philippe Roudot, Meghan K. Driscoll, Reto Fiolka, and Gaudenz Danuser.  Gordon Research Conference - Signaling by Adhesion Receptors.  Bates College, Lewiston, Maine, USA. 2016.
\item Kevin M. Dean, Philippe Roudot, Erik S. Welf, Meghan K. Driscoll, Reto Fiolka, and Gaudenz Danuser.  EMBO \& EMBL Symposium: Seeing is Believing - Imaging the Processes of Life.  EMBL, Heidelberg, Germany.  2015.
\item Kevin M. Dean, Jennifer L. Lubbeck, Premashis Manna, Lloyd M. Davis, Ralph Jimenez, Amy E. Palmer.  EMBO \& EMBL Symposium: Seeing is Believing - Imaging the Processes of Life.  EMBL, Heidelberg, Germany. 2013.
\item Kevin M. Dean, Jennifer L. Lubbeck, Lloyd M. Davis, Ralph Jimenez, Amy E. Palmer.  Signaling and Cellular Regulation Symposium.  University of Colorado, Boulder, CO, USA.  2013.
\item Kevin M. Dean, Jennifer L. Lubbeck, Lloyd M. Davis, Ralph Jimenez, Amy E. Palmer.  Computational, Optical, Sensing and Imaging.  University of Colorado, Boulder, CO, USA.  2013.
\item Kevin M. Dean, Jennifer L. Lubbeck, Lloyd M. Davis, Ralph Jimenez, Amy E. Palmer.  Computational Optical, Sensing and Imaging IAB Meeting.  Breckenridge, CO, USA.  2012.
\item Kevin M. Dean, Jennifer L. Lubbeck, Lloyd M. Davis, Ralph Jimenez, Amy E. Palmer.  Colorado Photonics Industry Association Annual Meeting.  Boulder, CO, USA. 2011.
\item Kevin M. Dean, Jennifer L. Lubbeck, Lloyd M. Davis, Ralph Jimenez, Amy E. Palmer.  Molecular and Cellular Biophysics Symposium at the University of Denver.  Denver, CO, USA. 2011.
\item Kevin M. Dean, Jennifer L. Lubbeck, Lloyd M. Davis, Ralph Jimenez, Amy E. Palmer.  Multiphoton Imaging: The Next 6$\times$10\textsuperscript{23} Femtoseconds, Janelia Farm, Howard Hughes Medical Institute.  Ashburn, VA, USA. 2010.
\item Kevin M. Dean, Jennifer L. Lubbeck, Hairong Ma, Ralph Jimenez, Amy E. Palmer.  New Optical Methods in Cell Physiology, Society of General Physiologists. Wood's Hole, MA, USA. 2010.
\item Kevin M. Dean, Jennifer L. Lubbeck, Hairong Ma, Ralph Jimenez, Amy E. Palmer.  Novel Approaches to Bioimaging II, Janelia Farm, Howard Hughes Medical Institute.  Ashburn, VA, USA. 2010.
\item Kevin M. Dean, Joseph C. Williamson, Student Scholarship Recognition Day, Salem, OR, USA. 2006.
\item Kevin M. Dean, Joseph C. Williamson, Northwest Undergraduate Science Research Conference at Oregon Health \& Science University, Portland, OR, USA. 2006.
\item Kevin M. Dean, Joseph C. Williamson, Student Scholarship Recognition Day, Salem, OR, USA. 2005. 
\end{enumerate}