\begin{etaremune}
\item Kang H, Choi JH, Sun Y, Mittal M, Korlakunta S, Pagani CA, Vishlaghi N, Somatilaka BN, Juan C, Nanes B, Lin HY, Bhatt K, Borges H, \textbf{Dean KM}, Lemoff A, Karner CM, Levi B. O-GlcNAcylation of a Phosphodegron-Proximal Site Rewires YAP Proteostasis and Cell Fate.

\item Chouhan S, Boujemaa-Paterski R, Munawar S, Bhatt K, German Do Nascimiento L, Li A, Ga\l{}ecki S, Rajendran D, Isogai T, \textbf{Dean KM}, Danuser G, Medalia O, Nanes BA. Keratin filaments and soluble vimentin interact with isoform specificity to organize cell signaling.

\item Ngo T, Faiyazuddin M, Nguyn TD, Haug J, Shen Q, Ga\l{}ecki S, Borges HM, Chen B, Wang X, Zhu H, Pappas SS, Voigt FF, Fiolka R, \textbf{Dean KM}. Altair-dvOPM: an open-access platform for large-field three-dimensional tissue imaging. bioRxiv [Preprint]. doi: 10.64898/2026.05.08.723912.

\item Backman V, Matei D, Zhang H, Wirtz D, Wood L, Fiolka R, \textbf{Dean KM}, Provenzano P, Eliceiri K. Cancer is a 4D Disease: Finding a Cure Demands New Cellular Imaging

\item Kamada S, Dang TT, Newman C, Sudderth J, Kim K, Parida PK, Llamas CB, Shen Q, Cai F, Yang C, Zacharias LG, Toffessi Tcheuyap V, Christie A, Hipsh S, Jackson B, Small C, Ghosh S, Reese T, Kim D, Kontoyiannis PD, Mathews TP, Halawa O, Lee J, Shmuel-Galia L, Mishra P, McDaniel P, Lin L, Margulis V, \textbf{Dean KM}, Zhang Q, Kapur P, DeBerardinis RJ, Brugarolas J, Malladi S. Organ-specific bioenergetic constraints define metastatic fitness in renal cell carcinoma.

\item Almasian M, Saberigarakani A, Zhang X, Brewer JA, Hameed R, Chai J, Lu Y, Ware SA, Zhou S, Wen Y, Lalami H, Hossein Beigi H, Yuan J, Liao J, \textbf{Dean KM}, Hong Y, Wu M, Tong D, Sapkota D, Ding Y. Mapping mesoscale cardiac architecture with axially swept dithered light-sheet microscopy.

\item Aleksandrovic E, Fross SR, Golomb SM, Ma W, Liu X, Zhao Z, Das NM, Reese TC, Borgez H, Tenekeci A, Yu L, Lopez J, Zhao M, Zhong Z, \textbf{Dean KM}, Lea J, Xu L, Stack MS, Zhang S. Tumor-intrinsic IFN$\gamma$ signaling and niche adaptation define an early colonization bottleneck in ovarian cancer metastasis.

\item Gihana GM, Bhatt K, Chang BJ, Murali V, Zhou F, Noh J, Ravishankar R, Borges H, Lin J, Oceguera J, Nogueira PA, Castro LP, Venkateswaran N, Chen B, Fiolka R, Conacci-Sorrell M, \textbf{Dean KM},Danuser G. Modulation of Oncogenic KRAS Signaling by Branched Actin-driven Cell Membrane Protrusions. bioRxiv [Preprint]. 2026 Apr 13:2026.04.09.717047. doi: 10.64898/2026.04.09.717047. PMID: 42039391; PMCID: PMC13104973.

\item Wu S, Chavula T, Calamai C, Wasser CR, Lazarrova I, Leal-Garcia M, Busson M, Peghaire C, Sacharidou A, Chen B, Fiolka R, \textbf{Dean KM}, Kounnas MZ, Herz J, Calvier L. A self-amplifying inflammatory loop driven by circulating Reelin sustains neurovascular dysfunction in Alzheimer’s disease.

\item Felan BL, Warshaw JN, Rivera AM, Hiremath C, Geshow K, Dean KM, Zhou FY, Moe OW, Carroll TJ, Chaney C, Miner JH, Marciano DK. Tubular COL4A5 drives epithelial dysfunction and survival in Alport syndrome. 

\item Xue Y, Merchant S, Reyes A, Luo M, Zhang R, Tippetts T, Grabowski G, Ngo T, Zhang Y, Shang Z, Jiang N, Jeffery E, Li Y, Wei T, Gu W, Du L, DeBerardinis RJ, \textbf{Dean KM}, Mathews TP, Lucas D, Zhao Z, Morrison SJ. Leptin Receptor \textsuperscript{+} cells create a perisinusoidal niche for thrombopoiesis in the bone marrow by synthesizing CXCL14. bioRxiv [Preprint]. 2026 Jan 28:2026.01.27.702029. doi: 10.64898/2026.01.27.702029. PMID: 41659692; PMCID: PMC12873943.

\item Baroody C, Sheth V, Calhoun H, Park J, Lin J, Eissa A, Marah M, Karami D, Means N, Lowe J, Mian M, Mathew J, Fiolka R, \textbf{Dean KM}, Wilhelm S. Multiscale imaging of nanoparticle spatiotemporal distributions in entire expanded multicellular cancer spheroids.

\item Ga\l{}ecki, S, Chang B-J, Zhou FY, Shen Q, Stoddard D, Chen B, Nicastro D, Fiolka R, \textbf{Dean KM\textsuperscript{‡}}. Unraveling Subcellular Ultrastructure with Cyclically Multiplexed Expansion Microscopy. bioRxiv [Preprint]. 2026 Jan 2:2026.01.01.697161. doi: 10.64898/2026.01.01.697161. PMID: 41509327; PMCID: PMC12776423.

\item Weems AD, Islam T, Borges H, Yapp C, Perez-Castro L, Nogueira P, Connerty-Marin Z, Lin J, Maliga Z, Lewis AJ, Kutter C, Mannino M, Vallius T, Santagata S, Morrison S, Sorger P, Conacci-Sorrell M, \textbf{Dean KM}, Danuser G. In vivo evidence for bleb-induced survival signaling in metastatic melanoma. bioRxiv [Preprint]. doi: 10.64898/2026.01.05.697601.

\item Chen B, Millett-Sikking A, Ga\l{}ecki S, Daetwyler S, Jiou J, Monistrol J, Shen Q, Zhou F, Lin HY, Jenkins E, Stein MC, Marlar-Pavey M, Sturm G, Li AL, Tang Q, Feng B, Diaz U, Chen Y, Shalizi A, Gillich A, Friedman JR, Tomer R, Chang BJ, Marshall WF, Shahmoradian S, \textbf{Dean KM}, Fiolka R. Multi-immersion Oblique Plane Microscope (miOPM): A reconfigurable platform for high-resolution Light-Sheet Fluorescence Microscopy. bioRxiv [Preprint]. 2025 Oct 6:2025.10.04.680473. doi: 10.1101/2025.10.04.680473. PMID: 41279040; PMCID: PMC12632540.

\item Isogai T, Murali VS, Zhou FY, Wang X, Rajendran D, Perez-Castro L, Nogueira PA, Borges H, Rajendran D, Venkateswaran N, \textbf{Dean KM}, Conacci-Sorrell M, Danuser G. Anchorage-independent cell proliferation promoted by fascin's F-actin bundling. bioRxiv [Preprint]. 2024 May 4:2024.05.04.592404. doi: 10.1101/2024.05.04.592404. PMID: 38746129; PMCID: PMC11092747.

\end{etaremune}