
\textit{High-School Students} \\
2021 -- 2022 \hspace{28pt} Samir Mamtani, Undergraduate Student, University of Wisconsin. \\
2021 -- 2022 \hspace{28pt} Sampath Rapuri, Undergraduate Student, Johns Hopkins University. \\
2021 -- 2022 \hspace{28pt} Renil Gupta, High-School Student, St. Marks H.S. \\
2019 -- 2019 \hspace{28pt} Ryan Hammond, Undergraduate Student, Carnegie Mellon University. \\

\textit{Undergraduate Students} \\
2023 -- Present \hspace{14pt} Cammy Kutter, Undegraduate Student, UCLA. \\
2023 -- Present \hspace{14pt} Sai Bommisetty, Graduate Student, ETH Zurich. \\
2023 -- Present \hspace{14pt} Joy Camposagrado, Undergraduate Student, UT Dallas. \\
2023 -- Present \hspace{14pt} James Harrigan, Undergraduate Student, UT Dallas. \\
2023 -- Present \hspace{14pt} Rayyan Sappayani, Undergraduate Student, UT Dallas. \\
2023 -- Present \hspace{14pt} Abhijeet Kulkarni, Undergraduate Student, UT Dallas. \\
2023 -- Present \hspace{14pt} Besher Nusair, Undergraduate Student, UT Dallas. \\
2023 -- 2023 \hspace{28pt} Evan Wylie, Undergraduate Student, Willamette University. \\
2012 -- 2013 \hspace{28pt} Jordan Gringauz, Legal Associate, Finnegan. \\
2011 -- 2013 \hspace{28pt} Derek Gann, Senior Devices Engineer, Heirloom. \\
2010 -- 2011 \hspace{28pt} Jennifer Binder, Graduate Student, Arizona State University. \\

\textit{Graduate Students} \\
2023 -- Present \hspace{14pt} Seweryn Gałecki, M.S., Fulbright Graduate Student. \\
2023 -- 2023 \hspace{28pt} Calvin Jones, Graduate Research Assistant, Boise State University. \\
2011 -- 2013 \hspace{28pt} Pramashis Manna, Assistant Professor, Ohio State University. \\

\textit{Postdoctoral Fellows} \\
2024 -- Present \hspace{14pt} Derek Abbott, Ph.D., UT Southwestern Medical Center. \\
2023 -- Present \hspace{14pt} Qionghua Shen, Ph.D., UT Southwestern Medical Center. \\
2023 -- Present \hspace{14pt} Dushyant Mehra, Ph.D., UT Southwestern Medical Center. \\
2023 -- Present \hspace{14pt} John Haug, Ph.D., UT Southwestern Medical Center. \\
2022 -- 2023 \hspace{28pt} Zach Marin, Ph.D., Postdoctoral Fellow, Max Perutz Labs Vienna. \\
2018 -- 2019 \hspace{28pt} Qiuyan Shao, Principal Data Scientist at Capital One. \\

\textit{Staff Scientists} \\
2023 -- Present \hspace{14pt} Samantha Calvache, Research Technician II, UT Southwestern Medical Center. \\
2022 -- Present \hspace{14pt} Xiaoding 'Annie' Wang, M.S., Software Engineer, UT Southwestern Medical Center. \\
2022 -- 2023 \hspace{28pt} Melissa Glidewell, Territory Manager, 89 North. \\
2021 -- Present \hspace{14pt} Jinlong Lin, Research Technician I, UT Southwestern Medical Center. \\
2021 -- Present \hspace{14pt} Hazel Borges, M.S., Research Assistant I, UT Southwestern Medical Center. \\
2021 -- 2023 \hspace{28pt} Dax Collision, Software Engineer, Atmos Energy. \\
2019 -- 2021 \hspace{28pt} Evgenia Azarova, Graduate Student, Johns Hopkins University. \\
2018 -- 2020 \hspace{28pt} Saumya Vora, M.S., Regulatory Affairs Specialist, Medtronic. \\
2017 -- 2019 \hspace{28pt} Justin Cillay, M.D., Resident Physician, University of Colorado. \\
2012 -- 2014 \hspace{28pt} Pia Friis,  Laboratory Technician in Clinical Microbiomics. \\


