%Consistently evaluated as a 'good' or 'excellent'  instructor with especially high marks for preparation of course material, clarity of presentation, level of challenge, and style of presenter. Majority of students communicated interest in taking further courses in the future. 
%\vspace{4pt}
2025 \hspace{58pt} Course Director, Scalable Data Analysis with Dask, UTSW. \\
2025 \hspace{58pt} Course Director, Introduction to Python Software Development on GitHub, UTSW. \\
2025 \hspace{58pt} Discussion Group Leader, Responsible Conduct of Research, UTSW. \\ 
2024 \hspace{58pt} Course Director, Introduction to Python, UTSW. \\
2024 \hspace{58pt} Lecturer, Optical Imaging and Probe Engineering, UTSW. \\
2023 \hspace{58pt} Course Director, Introduction to Python Software Development on GitHub, UTSW. \\
2022 \hspace{58pt} Discussion Group Leader, Responsible Conduct of Research, UTSW. \\ 
2022 \hspace{58pt} Assistant Instructor, Computational Image Analysis, UTSW. \\
2021 \hspace{58pt} Assistant Instructor, Computational Image Analysis, UTSW. \\
2018 \hspace{58pt} Assistant Instructor, Optical Microscopy, UTSW. \\
2017 \hspace{58pt} Assistant Instructor, Optical Microscopy, UTSW. \\
2016 \hspace{58pt} Assistant Instructor, Optical Microscopy, UTSW. \\
2015 \hspace{58pt} Assistant Instructor, Optical Microscopy, UTSW. \\
2013 \hspace{58pt} Laboratory Assistant, Light Microscopy, University of Colorado. \\
2007 \hspace{58pt} Teaching Assistant, Introductory Chemistry, University of Colorado.  \\
2006 \hspace{58pt} Tutor, Introductory Chemistry and Physical Chemistry, Willamette University. \\
\\ 
%\vspace{6pt}